Embedded Domain Specific Languages inside Functional Languages

### 2014-03-14 paper.tex
Adding figures from other computer.

There are two fundamental types of Domain Specific Languages
(Figure X).
%
The first, like the SQL example, is a first class language,
with its own compiler or interpreter, and is often used in
its own ecosystem. (Figure X, (1)) 
All the examples mentioned so far fall
into this category. The primary difference between SQL and
(say) Java is one of scope and focus, though sometimes
DSLs grow to be as large are general purpose languages.
%
The other class of Domain Specific Languages are languages
embedded inside another hosting language. Such languages
can have the look and feel of being their own languages,
but leverage the host language to provide an existing
eco-structure and initial semantics. It is this second
class of DSLs we are interested in, and is the subject of
this paper.

\begin{figure}

\vskip 1in        
((FIGURE ABOUT DSL))

\end{figure}

@@

\begin{figure}[!t]
  \centering
        XXXX
  \caption{Shallow and Deep Embedding of Arithmetic}
  \label{fig:counter-pictureX}
%  \vspace{-0.1in}
\end{figure}

@@

\cursor{}

>>>>

There are two fundamental types of Domain Specific Languages
(Figure~\ref{fig:types-of-dsls}).
%
The first, like the SQL example, is a first class language,
with its own compiler or interpreter, and is often used in
its own ecosystem. (Figure \ref{fig:types-of-dsls}(1)) 
All the examples mentioned so far fall
into this category. The primary difference between SQL and
(say) Java is one of scope and focus, though sometimes
DSLs grow to be as large are general purpose languages.
%
The other class of Domain Specific Languages are languages
embedded inside another hosting language. Such languages
can have the look and feel of being their own languages,
but leverage the host language to provide an existing
eco-structure and initial semantics. 
(Figure \ref{fig:types-of-dsls}, (2))
It is this second
class of DSLs we are interested in, and is the subject of
this paper.

\begin{figure}[!t]
  \centering        
  \includegraphics[width=0.4\textwidth]{images/TypesOfDSLs.pdf}
  \caption{Types of Domain Specific Languages}
  \label{fig:types-of-dsls}
\end{figure}

@@

\begin{figure}[!t]
  \centering        
  \includegraphics[width=0.6\textwidth]{images/DeepEmbedding.pdf}
  \caption{Shallow and Deep Embedding of Arithmetic}
  \label{fig:deep-dsls}
\end{figure}

@@
